---
title: "GoogleSearch"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Google search results comparison
Our goal here was to observe the variation of the number of results of a single word google search depending of the size of the word.

Firstly we sent 300 request for each of the eleven languages we compared and extracted the number of results from each answer.


We then compared it as a colored dot cloud and then computed the mean of number of results for each request size.

Our main observation was that for every langague there are really high spikes for small words. And that the number of results seems to decrease from length 3 to 10 and then looks random.

```{r}
df_ch = read.csv("saves/concat/CH-dic.txt.out")
df_ch$lang = "CH"
library(ggplot2)
df_dk = read.csv("saves/concat/DK-dic.txt.out")
df_dk$lang = "DK"
df_uk = read.csv("saves/concat/UK-dic.txt.out")
df_uk$lang = "UK"

total <- rbind(df_ch,df_dk)
total <- rbind(total,df_uk)
ggplot(total, aes(x = tailleMot, y = nbResults, color=lang)) + geom_point()
total_petit = total[total$nbResults < 5000000000,]
ggplot(total_petit, aes(x = tailleMot, y = nbResults, color=lang)) + geom_point()
total_petit_2 = total[total$nbResults < 100000000,]
ggplot(total_petit_2, aes(x = tailleMot, y = nbResults, color=lang)) + geom_point()

```

```{r echo=FALSE}
df_de = read.csv("saves/concat/DE-dic.txt.out")
df_de$lang = "DE"
total <- rbind(total,df_de)

df_en = read.csv("saves/concat/EN-dic.txt.out")
df_en$lang = "EN"
total <- rbind(total,df_en)

df_es = read.csv("saves/concat/ES-dic.txt.out")
df_es$lang = "ES"
total <- rbind(total,df_es)

df_fr = read.csv("saves/concat/FR-dic.txt.out")
df_fr$lang = "FR"
total <- rbind(total,df_fr)

df_it = read.csv("saves/concat/IT-dic.txt.out")
df_it$lang = "IT"
total <- rbind(total,df_it)

df_nl = read.csv("saves/concat/NL-dic.txt.out")
df_nl$lang = "NL"
total <- rbind(total,df_nl)

df_us = read.csv("saves/concat/US-dic.txt.out")
df_us$lang = "US"
total <- rbind(total,df_us)

```

```{r}

library(plyr)
summ = ddply(total,c("tailleMot","lang"),summarize,num = length(nbResults), mean_results = mean(nbResults), sd_results = sd(nbResults));
summ_us = ddply(df_us,c("tailleMot","lang"),summarize,num = length(nbResults), mean_results = mean(nbResults), sd_results = sd(nbResults));

df_no = read.csv("saves/concat/NO-dic.txt.out")
df_no$lang = "NO"
total <- rbind(total,df_no)


ggplot(total, aes(x = tailleMot, y = nbResults, color=lang)) + geom_point()
total_petit = total[total$nbResults < 5000000000,]
ggplot(total_petit, aes(x = tailleMot, y = nbResults, color=lang)) + geom_point()
total_petit_2 = total[total$nbResults < 100000000,]
ggplot(total_petit_2, aes(x = tailleMot, y = nbResults, color=lang)) + geom_point()

ggplot(summ, aes(x = tailleMot, y = mean_results, color=lang)) + geom_line()
ggplot(summ_us, aes(x = tailleMot, y = mean_results)) + geom_line()

```

